Co-moving stars in \textsl{Gaia DR1}:\\ An abundance of very wide separation co-moving pairs

### 2017-04-04 paper/ms.tex
simplify statement

\begin{eqnarray}
  \ln p(\vec{v}) = -\frac{1}{2}\,\ln||2\pi\,\mat{V}_m||
  -\frac{1}{2} \transp{\vec{v}}\,\inv{\mat{V}_m}\,\vec{v}
\end{eqnarray}
We can identify $\mat{A}$, $\mat{B}\,\vec{b}$, and $C$ in
$\ln p(\vec{v}) + \ln p(\data \given \vec{v}, r_i, r_j)$, and write down
$\vec{\nu}$ and $\Delta$ using \eqname~\ref{eq:convnu} and \ref{eq:convDelta} as

>>>>

\begin{eqnarray}
  \ln p(\vec{v}) = -\frac{1}{2}\,\ln||2\pi\,\mat{V}_m||
  -\frac{1}{2} \transp{\vec{v}}\,\inv{\mat{V}_m}\,\vec{v}
\end{eqnarray}
We can identify $\vec{\nu}$ and $\Delta$ in
$\ln p(\vec{v}) + \ln p(\data \given \vec{v}, r_i, r_j)$
using \eqname~\ref{eq:convnu} and \ref{eq:convDelta} as
